---
title: "Exploratory analysis of Italian cafes names"
author: "Stefano De Sabbata"
date: "`r lubridate::now()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aims

Work in progress! :sweat_smile:

The aim is to conduct an analysis similar to the work presented by Chris Brunsdon, Paul Harris and Lex Comber at [GIRSRUK 2022](http://liverpool.gisruk.org/), in the paper [*"A Spatial Analysis of British Public House Names"*](https://doi.org/10.5281/zenodo.6410180), but focusing on *Italian "cafes"*. However, for a number of cultural and historical reasons, *Italian "cafes"* can be understood and encoded in OpenStreetMap (the data source for this project) as: `amenity => cafe`, `amenity => bar`, `shop => bakery`, `shop => confectionery`, `shop => chocolate`, `amenity => ice_cream` or `shop => ice_cream`. This will definitely need to be discussed here at some point -- likely, this has already been discussed somewhere else.


## Preparation

### Libraris

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(magrittr)
library(knitr)
library(sf)
library(tmap)
#library(ggmap)
library(leaflet)
library(tidytext)
```

### Data

This analysis uses OpenStreetMap open data, licensed under the Open Data Commons Open Database License (ODbL) 
by the OpenStreetMap Foundation (OSMF) © OpenStreetMap contributors.

```{r data}
barcafes_Italy <- read_sf("../data/bar-cafe-etc-Italy-2022-04-09-19-36-39.geojson")
```

### Overview map

```{r, fig.height=6.5, fig.width=5}
tm_shape(barcafes_Italy) + 
  tm_dots("osm_type", size= 0.01, alpha = 0.5, palette = "Set1") +
  tm_credits("© OpenStreetMap contributors")
```


## Text content overview

```{r}
stop_words_it <- tibble(
  word = stopwords::stopwords("it", source = "snowball"),
  lexicon = "snowball"
)
```

```{r}
barcafes_Italy_name_tokens <-
  barcafes_Italy %>% 
  st_drop_geometry() %>% 
  filter(!is.na(name)) %>% 
  unnest_tokens(word, name)
```

Most common words in *Italian "cafes"* names.

```{r}
barcafes_Italy_name_tokens %>% 
  anti_join(stop_words_it) %>% 
  count(word, sort = TRUE) %>% 
  slice_max(order_by = n, n = 100) %>% 
  kable()
```

## Name components' odds ratio

In order to explore how specific to each area a part of a name is, I start by following the approach used by Shelton et al. (2014), calculating the odd-ratio (or location quotient) for each word and area, unsing a 10km hexagonal grid.

```{r}
hex_gird <- read_sf("../data/hexagonal_grid_10km_Italy.geojson")
```

```{r}
barcafes_Italy_with_hex <-
  barcafes_Italy %>% 
  st_join(hex_gird)
```

```{r}
barcafes_Italy_with_hex_tokens <-
  barcafes_Italy_with_hex %>% 
  st_drop_geometry() %>% 
  filter(!is.na(name)) %>% 
  unnest_tokens(word, name) %>% 
  anti_join(stop_words_it) %>% 
  count(hex_id, word, sort = TRUE) %>%
  complete(hex_id, word, fill = list(n = 0))

sum_hex <- barcafes_Italy_with_hex_tokens %>% count(hex_id, wt = n) %>% rename(sum_hex = n)
sum_word <- barcafes_Italy_with_hex_tokens %>% count(word, wt = n) %>% rename(sum_word = n)
sum_all_value <- barcafes_Italy_with_hex_tokens %>% count(wt = n) %>% pull(n)

barcafes_Italy_with_hex_oddratios <-
  barcafes_Italy_with_hex_tokens %>% 
  left_join(sum_hex) %>% 
  left_join(sum_word) %>% 
  mutate(sum_all = sum_all_value) %>% 
  mutate(
    oddratio = ((n / sum_word) / (sum_hex / sum_all))
  ) %>% 
  mutate(
    oddratio_lower = 
      exp(
        log(oddratio) - 
          (3.29 * sqrt(
            (1/n) + (1/sum_word) + (1/sum_hex) + (1/sum_all)
          ))
      )
  )
```

Odds ratio base descriptive statistics for top name components.

```{r}
barcafes_Italy_name_tokens %>% 
  anti_join(stop_words_it) %>% 
  count(word, sort = TRUE) %>% 
  slice_max(order_by = n, n = 100) %>% 
  left_join(
    barcafes_Italy_with_hex_oddratios %>% 
      group_by(word) %>% 
      summarise(
        oddratio_min = min(oddratio),
        oddratio_mean = mean(oddratio),
        oddratio_median = median(oddratio),
        oddratio_max = max(oddratio),
        oddratio_sd = sd(oddratio)
      )
  ) %>% 
  kable()
```


## Term-specific maps

### Pasticceria

```{r}
leaflet(
    barcafes_Italy %>% 
    filter(
      name %>% 
        str_to_lower() %>% 
        str_detect("pasticceria")
    )
  ) %>%
  addTiles() %>%
  addProviderTiles(providers$Stamen.Toner) %>% 
  addCircleMarkers(
    radius = 5,
    color = "red",
    popup = ~as.character(name), 
    label = ~as.character(name)
  )
```

```{r}
# tm_shape(boundary_Italy) + 
#   tm_borders() +
tm_shape(
    hex_gird %>% 
      inner_join(
        barcafes_Italy_with_hex_oddratios %>% 
          filter(word == "pasticceria")
      )
  ) +
  tm_fill(
    "oddratio_lower", 
    showNA = FALSE, palette = "YlOrRd", n=9, style = "jenks"
  )
```

# Pane

```{r}
leaflet(
    barcafes_Italy %>% 
    filter(
      name %>% 
        str_to_lower() %>% 
        str_detect("pane")
    )
  ) %>%
  addTiles() %>%
  addProviderTiles(providers$Stamen.Toner) %>% 
  addCircleMarkers(
    radius = 5,
    color = "red",
    popup = ~as.character(name), 
    label = ~as.character(name)
  )
```

```{r}
# tm_shape(boundary_Italy) + 
#   tm_borders() +
tm_shape(
    hex_gird %>% 
      inner_join(
        barcafes_Italy_with_hex_oddratios %>% 
          filter(word == "pane")
      )
  ) +
  tm_fill(
    "oddratio_lower", 
    showNA = FALSE, palette = "YlOrRd", n=9, style = "jenks"
  )
```

### Forno

```{r}
leaflet(
    barcafes_Italy %>% 
    filter(
      name %>% 
        str_to_lower() %>% 
        str_detect("forno")
    )
  ) %>%
  addTiles() %>%
  addProviderTiles(providers$Stamen.Toner) %>% 
  addCircleMarkers(
    radius = 5,
    color = "red",
    popup = ~as.character(name), 
    label = ~as.character(name)
  )
```

```{r}
# tm_shape(boundary_Italy) + 
#   tm_borders() +
tm_shape(
    hex_gird %>% 
      inner_join(
        barcafes_Italy_with_hex_oddratios %>% 
          filter(word == "forno")
      )
  ) +
  tm_fill(
    "oddratio_lower", 
    showNA = FALSE, palette = "YlOrRd", n=9, style = "jenks"
  )
```

### Centrale

```{r}
leaflet(
    barcafes_Italy %>% 
    filter(
      name %>% 
        str_to_lower() %>% 
        str_detect("centrale")
    )
  ) %>%
  addTiles() %>%
  addProviderTiles(providers$Stamen.Toner) %>% 
  addCircleMarkers(
    radius = 5,
    color = "red",
    popup = ~as.character(name), 
    label = ~as.character(name)
  )
```

```{r}
# tm_shape(boundary_Italy) + 
#   tm_borders() +
tm_shape(
    hex_gird %>% 
      inner_join(
        barcafes_Italy_with_hex_oddratios %>% 
          filter(word == "centrale")
      )
  ) +
  tm_fill(
    "oddratio_lower", 
    showNA = FALSE, palette = "YlOrRd", n=9, style = "jenks"
  )
```



## References

Brunsdon, Chris, Harris, Paul, & Comber, Alexis. (2022, March 30). A Spatial Analysis of British Public House Names. 30th Annual Geographical Information Science Research UK (GISRUK), Liverpool, United Kingdom. [https://doi.org/10.5281/zenodo.6410180](https://doi.org/10.5281/zenodo.6410180)

Shelton, T., Poorthuis, A., Graham, M., & Zook, M. (2014). Mapping the data shadows of Hurricane Sandy: Uncovering the sociospatial dimensions of ‘big data’. Geoforum, 52, 167-179. [https://doi.org/10.1016/j.geoforum.2014.01.006](https://doi.org/10.1016/j.geoforum.2014.01.006)
